---
title: "bagging"
author: "issa fall"
date: "January 1, 2016"
output: html_document
---
##Bagging
Basic idea:
-1.Resample cases and recalculate predictions
-2.Average or majority vote
Notes
-similar bias
-Reduced variance
-More useful for non-linear functions
Ozone data 
```{r,echo=TRUE}
library(caret)
library(ElemStatLearn)
library(party)
data(ozone, package = "ElemStatLearn")
ozone<-ozone[order(ozone$ozone), ]
head(ozone)
ll<-matrix(NA,nrow = 10, ncol = 155)
for(i in 1:10){
  ss<-sample(1 : dim(ozone)[1], replace = T)
  ozone0<-ozone[ss, ]
  ozone0<-ozone0[order(ozone0$ozone), ]
  loess0<-loess(temperature ~ ozone, data = ozone0, span = 0.2)
  ll[i, ]<-predict(loess0, newdata =data.frame(ozone = 1:155))
}
```
##Bagged loess
```{r,echo=TRUE}
plot(ozone$ozone, ozone$temperature, pch =19, cex =0.5)
for(i in 1:10){lines(1:155, ll[i, ],col ="grey", lwd =2)}
lines(1:155, apply(ll, 2, mean), col ="red", lwd =2)
```


##Bagging in caret
-some models perform bagging for you,in  "train()"function consider "method" options
-bagEarth
-treebag
-bagFDA
-Alternatively you can bag any model you chose using the "bag()"function
```{r,echo=TRUE}
predictors<-data.frame(ozone = ozone$ozone)
temperature =ozone$temperature
treebag<-bag(predictors,temperature, B =10,
             bagControl = bagControl(fit = ctreeBag$fit,
                                     predict = ctreeBag$pred,
                                     aggregate = ctreeBag$aggregate))
```
##Example of custum bagging(continued)
```{r,echo=TRUE}
plot(ozone$ozone, temperature, col ="lightgrey", pch =19)
points(ozone$ozone, predict(treebag$fits[[1]]$fit, predictors), pch =19, col ="red")
points(ozone$ozone, predict(treebag, predictors), pch =19, col ="blue")
