---
title: "google"
author: "issa fall"
date: "December 27, 2015"
output: html_document
---
##google stock
```{r,echo=TRUE}
library(quantmod)
library(timeSeries)
library(timeDate)
library(xts)
library(TTR)
library(zoo)
library(expsmooth)
from.dat<-as.Date("01/01/09", format= "%m/%d/%y")
to.dat<-as.Date("12/31/14", format ="%m/%d/%y")
getSymbols("GS", src ="google", from =from.dat, to =to.dat)
head(GS)
periodicity(GS)
getSymbols("GS", src = "google", from =from.dat, to =to.dat)
head(GS)
periodicity(GS)
apply.weekly(GS, FUN = function(x){max(Cl(x))})
```
##Summarise monthly and store as time series
```{r,echo=TRUE}
mGoog<-apply.monthly(GS, FUN = function(x){max(Op(x))})
mGoog
##googOpen<-Op(mGoog)
ts1<-ts(mGoog, frequency = 12)
plot(ts1, xlab = "Years+1", ylab = "GS")
```

##Example of time series decomposition into parts
```{r,echo=TRUE}
plot(decompose(ts1), xlab = "Years+1")
```


##Training and test sets
```{r,echo=TRUE}
ts1Train<-window(ts1, start = 1, end = 5)
ts1Test<-window(ts1, start = 5, end = (7-0.1))
ts1Train
dim(ts1Train);dim(ts1Test)
```
##Simple moving average
```{r,echo=TRUE}
plot(ts1Train)
lines(ma(ts1Train, order =3), col ="red")
```


##Simple exponential smoothing
```{r,echo=TRUE}
ets1<-ets(ts1Train, model ="MMM")
fcast<-forecast(ets1)
plot(fcast);lines(ts1Test, col ="red")
```


##Get the accuracy
```{r,echo=TRUE}
accuracy(fcast, ts1Test)
```

##Summarise weekly and store as time series
```{r,echo=TRUE}
getFX("USD/EUR")
mUS<-to.weekly(USDEUR)
mUS
USOpen<-Op(mUS)
USOpen
ts1<-ts(USOpen, frequency = 7)
ts1
plot(ts1,xlab = "Weeks+1",ylab = "USDEUR")
```


##Decompose a time series into parts
```{r,echo=TRUE}
plot(decompose(ts1),xlab = "Week+1")
```


##Training and test sets
```{r,echo=TRUE}
ts1Train<-window(ts1, start = 1, end = 5)
ts1Test<-window(ts1, start = 5, end = (7-0.01))
ts1Train
```
##Forecasting:choice between simple moving average and simple exponential smoothing
##Simple moving average
```{r,echo=TRUE}

plot(ts1Train)
lines(ma(ts1Train, order =3),col ="red")
```
##Simple exponential smoothing
```{r,echo=TRUE}
ets1<-ets(ts1Train, model ="MMM")
fcast<-forecast(ets1)
plot(fcast);lines(ts1Test, col ="red")
```


##Get accuracy
```{r,echo=TRUE}
accuracy(fcast,ts1Test)
```
##Microsoft stock
```{r,echo=TRUE}
library(dygraphs)
quantmod::getSymbols("MSFT", from = "2014-06-01", auto.assign = TRUE)
ret = ROC(MSFT[, 4])
mn = mean(ret, na.rm = TRUE)
sdt = sd(ret, na.rm = TRUE)
dygraph(ret, main ="Microsoft Share Price") %>%
  dySeries("MSFT.Close", label ="MSFT") %>%
  dyShading(from = mn - sdt, to = mn + sdt, axis ="y") %>%
  dyRangeSelector()

dygraph(MSFT)%>%
  dyRangeSelector()

```
##Lung Death in UK

```{r,echo=TRUE}
lungDeaths<-cbind(ldeaths, mdeaths,fdeaths)
dygraph(lungDeaths, main = "Death from lung Disease(UK)") %>%
  dyRangeSelector()
```

##Predicting lung deaths in UK

```{r,echo=TRUE}
hw<-HoltWinters(ldeaths)
p<-predict(hw, n.ahead = 36, prediction.interval = TRUE)
all<-cbind(ldeaths, p)

dygraph(all, main = "Death from lung Disease in UK") %>%
  dySeries("ldeaths", label = "Actual") %>%
  dySeries(c("p.lwr", "p.fit", "p.upr"), label = "Predicted")
```
##Mcrosoft and HPQ share prices
```{r,echo=TRUE}
getSymbols(c("MSFT","HPQ","WMT"), from = "2014-06-01", auto.assign = TRUE)

stocks<-cbind(MSFT[, 2:4], HPQ[, 2:4], WMT[, 2:4])
dygraph(stocks, main = "Microsoft and HPQ share Prices") %>%
dySeries(c("MSFT.Low", "MSFT.Close","MSFT.High"), label = "MSFT") %>%
  dySeries(c("HPQ.Low", "HPQ.Close", "HPQ.High"), label = "HPQ") %>%
  dySeries(c("WMT.Low", "WMT.Close", "WMT.High"), label = "WMT")%>%
  dyRangeSelector()
```




